Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise

### 2016-09-05 main.tex
Rewritten section on cognitive priming

This article attempts to address the issue with a different experimental design
and a novel methodology to measure \emph{in-the-moment} anthropomorphic
attributions.  Our approach is built on a combination of cognitive priming and
eye-tracking. By doing so, we evidence specific gaze fixations on the head
of the robot when the participants are primed with higher expectations
regarding the cognitive skills of the robot. We then establish the link
between head fixations and anthropomorphic ascriptions, to eventually show how
subtle interaction manipulations do significantly impact our tendency
to ascribe human traits to machines.

Previous studies had shown that cognitive and/or affective priming influences
human perception of the input stimulus. \cite{zajonc1980feeling} advocated the
the use of affective priming and proposed that the affective reactions can be
elicited with minimal stimulated input. As \cite{murphy1993affect} wrote
\textit{``The experimental paradigm of priming, involves the presentation of one
stimulus, or prime, alters subjects' perceptions of a second target
stimulus...''}  \cite{murphy1993affect} found in their series of studies, where
the subjects were shown happy and angry faces of people as a priming method,
showed that the subjects' perceptions of positive emotions were higher and
quicker when the priming was a happy face than for those who were primed with a
angry face. The gender of the priming faces, however had no effect on the
subjects' perception.

\cite{forgas1987mood} showed that priming subjects with positive or negative
moods affects their person-perception judgement\footnote{Person-perception
judgement is a task where the subjects are asked to read a few characteristics
of an unknown person; and once they have read the description the subjects are
then asked to provide their perception about the target person}. In their study,
\cite{forgas1987mood} showed used a bogus test with manipulated positive or
negative feedback to prime the mood of the subjects in a positive or negative
manner. Once the subjects were primed with a particular mood they were shown the
descriptions of some unknown persons (with the same positive and negative
characteristics). The results showed that the mood priming influences their
person-perception, i.e, the positively primed subjects gave more positive
remarks about the target perception while the negatively primed subjects gave
more negative remarks. Moreover, the subjects in both the priming conditions
spent more time on the priming specific characteristics (positive or negative).
This shows that not only subjects' perception was altered but also their
approach as well using the mood priming.

\cite{yi1990cognitive} used specific attributes of a car to prime subjects'
before they watched an advertisement about cars. The advertisement focused on
explains various characteristics of a few imaginary cars in terms of the safety
and the fuel efficiency. The priming stimulus had the size of the cars
manipulated. The results showed that tone (affective priming) and size
(cognitive priming) affects the favourability of the cars. For example, a big
car was perceived to be more ``safe'' and less ``fuel-efficient'' than the small
cars.

\cite{tillmann2006cognitive}, in an fMRI study with music notes, showed that
different parts of the frontal cortex gets activated when the participants were
primed with sung or instrumental music. In their experiment, the subjects were
asked to listen the first seven notes in either sung or instrumental manner
(cognitive priming) and then to identify the relation between the first seven
and the eighth note. The results showed that the subjects showed a higher
activation in the inferior frontal cortex when primed with the sung notes than
when they were primed with the instrumental notes. \cite{rholes1987emotional}
showed that the memory recall is affected by the tone (affective priming) of the
self-evaluation statement. In an experiment, where the subjects were given a set
of positive or negative self-evaluation statements before being asked to recall
a few good and bad memories from their past, the subjects were faster in
recalling good memories when they were given a positive self-evaluation test;
and vice-versa.

All the above studies show that the cognitive and/or affective priming might
alter the behaviour and/or the perception of the subjects about a target
stimulus. Some of the studies found some complex interactions between cognitive
and affective priming (\cite{yi1990cognitive} and \cite{storbeck2008affective}
). In this contribution, we were only interested in the cognitive priming aspect
during a Human Robot Interaction situation, as \cite{baldwin1990priming}
advocated that the cognitive priming may activate a relationship schema between
the priming stimulus and the target stimulus. Moreover, in the context of
advertisement, a number of studies suggest that the ad context (cognitive
priming) can influence the audience's perception of the ad, and thus, its
effectiveness (e.g., \cite{singh1987arousal};\cite{soldow1981response})  Our
primary hypothesis was that the way the robot is given commands might alter the
way the subjects perceive its actions. We propose to use a neutral mood (no
affective priming) and two cognitive priming conditions (Human-like and
Machine-like), in order to remove the ``mood'' or  ``affect'' bias of the
priming. The ``machine-like'' priming consisted of giving commands to the robot
which are more ``machine-like''. On the other hand, the ``human-like'' priming
had the commands to robot in a more ``human-like'' manner (Manipulation-check
hypothesis). We also kept the time of priming to be the same in the human-like
and machine-like conditions, in order to remove the time of priming effect on
the subjects' perceptions about the robot.

@@

@@

This study is built as an eye-tracking experiment (using a stationary
eye-tracker SMI RED 250) where participants watch short videos of an agent --
either a robot (Aldebaran Robotics' Nao) or a human -- performing simple tasks
(picking an object or pointing toward a sound source) after being primed.  The
priming is designed to elicit either low cognitive ascriptions onto the robot
(leading to what we call hereafter a \emph{machine-like} interaction situation)
or richer cognitive ascriptions (leaning toward what we call a \emph{human-like}
interaction situation).

@@

\section{Conclusion}
\labe{conclusion}

>>>>

This article introduces a different experimental design and a novel methodology
to measure \emph{in-the-moment} anthropomorphic attributions.  Our approach is
built on a combination of cognitive priming and eye-tracking. By doing so, we
evidence specific gaze fixations on the head of the robot when the participants
are primed with higher expectations regarding the cognitive skills of the robot.
We then show how subtle interaction manipulations do significantly impact our
tendency to ascribe human traits to machines, to eventually establish the link
between head fixations and anthropomorphic ascriptions.

@@

Cognitive priming is the primary mean of condition manipulation that we rely on.
Many previous studies have investigated how cognitive and/or affective priming
influence human perception of an input stimulus. \cite{zajonc1980feeling}
advocated the use of affective priming and proposed that the affective reactions
can be elicited with minimal stimulated input: \cite{murphy1993affect} found in
a series of studies where participants were shown happy and angry faces as a
priming method, that the participants' perceptions of positive emotions were
higher and quicker when the priming was a happy face than for those who were
primed with a angry face. The gender of the priming faces, however had no effect
on the participants' perception.

\cite{forgas1987mood} showed that priming participants with positive or negative
moods affects their person-perception judgement\footnote{Person-perception
judgement is a task where the participants are asked to read a few
characteristics of an unknown person; and once they have read the description
the participants are then asked to provide their perception about the target
person}. In their study, they used a test with manipulated positive or negative
feedback to prime the mood of the participants in a positive or negative manner.
The results showed that the priming influenced their person-perception, \ie the
positively primed participants provided more positive remarks about a new,
unknown face, while the negatively primed participants made more negative
remarks. Moreover, the participants in both the priming conditions spent more
time elaborating on the specific characteristics they were primed with. This
shows that mood priming influenced not only the participants' perceptions, but
also their behaviours during the test.

Similarly, \cite{yi1990cognitive} used specific attributes of a car to prime
participants before they watched an advertisement about cars. The advertisement
discussed characteristics of imaginary cars in terms of their safety and fuel
efficiency.  The priming stimulus had manipulated the size of the car, as well
as the tone of the description. The results showed that both the tone (affective
priming) and the size (cognitive priming) affects the likeability of the car.
In the context of advertising, a number of studies suggest that the context
(cognitive priming) influences the perception of the advertisement by the
audience, and therefore, its effectiveness~\citep{singh1987arousal,soldow1981response}.

In an fMRI study with music notes, \cite{tillmann2006cognitive} showed that
different parts of the frontal cortex gets activated when the participants were
primed with sung or instrumental music. In their experiment, the participants were
asked to listen the first seven notes in either sung or instrumental manner
(cognitive priming) and then to identify the relation between the first seven
and the eighth note. The results showed that the participants showed a higher
activation in the inferior frontal cortex when primed with the sung notes than
when they were primed with the instrumental notes.

\cite{rholes1987emotional} showed that the memory recall is affected by the tone
(affective priming) of self-evaluation statement: In an experiment, where
the participants were given a set of positive or negative self-evaluation
statements before being asked to recall a few good and bad memories from their
past, the participants were faster in recalling good memories when they were
given a positive self-evaluation test and vice-versa.

All the above studies show that cognitive and/or affective priming can alter
both the perception by the participant of a target stimulus, and the behaviour
of the participant while processing the stimulus. Some of the studies also
evidenced interactions between cognitive and affective
priming~\citep{yi1990cognitive,storbeck2008affective}.

We focus here on cognitive priming: as~\cite{baldwin1990priming} pointed out, we
expect that cognitive priming may activate a relationship schema between the
priming stimulus (the context of the interaction) and the
target stimulus (the interaction situation, and in particular, the robot).
More specifically, we designed stimuli in which the way the robot is given
commands pre-supposes a specific interaction situation (more or less
`human-like') and is expected in turn to alter the way the participants perceive the
actions of the robot.

We use a neutral mood/tone (no affective priming) and, as detailed in the
Methodology section hereafter, two cognitive priming conditions (hereafter
referred as `machine-like' and `human-like').

@@

As mentioned, this study is built as an eye-tracking experiment (using a stationary
eye-tracker SMI RED 250) where participants watch short videos of an agent --
either a robot (the Aldebaran Robotics' Nao) or a human -- performing simple tasks
(picking an object or pointing toward a sound source) after being primed.  The
priming is designed to elicit either low cognitive ascriptions onto the robot
(leading to what we call hereafter a \emph{machine-like} interaction situation)
or richer cognitive ascriptions (leading to what we call a \emph{human-like}
interaction situation).

@@

\section{Conclusion}
\label{conclusion}
